---
title: "Project Document"
author: "Aaron Gould, Lila Craveiro, Danielle Freshwaters"
date: "11/20/2019"
output:
  html_document:
    keep_md: yes
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(faraway) #NEW! Be sure to install this package!
library(Sleuth3) #NEW! Need to install this to access the data!
library(GGally)
library(tidyverse)
library(ggridges)
library(fivethirtyeight)
```


## Cabinet Turnover Data

1) Introduce your data and research question. Make sure you include a graph/table that summarizes the response variable. Tell us about the important predictor variables you will be evaluating.

Question: We will be analyzing the data set **cabinet_turnover** from the **fivethirtyeight** package.  This data set includes variables taken from 7 different presidencies, from Jimmy Carter to Donald Trump, summarizing turnover in each of their cabinets.  Our question is: What factors effect the length of an appointee's cabinet tenure?  We will be evaluating how *position* (the cabinet position), *president* (the sitting president), and a variable of our own creation *XXX* (number of days into the administration the appointee started) affect *length_proportion* (another variable we created that gives us the proportion of *length* to the total number of days an appointee could have served).  

2) Exploratory work and basic models

```{r}
ggplot(cabinet_turnover) + geom_boxplot(aes(x=president, y= length))
```
We are curious to see how the length each appointee spends in their position depends on the president in office. We will need to take in to account the number of terms each president served and the time that our current president has been in office (this data was taken at Trump's midterm). Without taking that into account we can se that Obama had the highest median for the length an appointee spent in their cabinet position.    


```{r}
ggplot(cabinet_turnover) + geom_jitter(aes(x=president, y= days))
```
We are interested in examining what happened during the dates that we see clusters of appointees leaving their position. We would like to examine, outside of this data set, what events occured to cause this. We noticed that most appointees leave at either 4 years or 8 years into the presidency.


***I think we can get rid of this graph??  


```{r}
ggplot(cabinet_turnover) + geom_boxplot(aes(x=position, y= length))
```

I wanted to see how many only had one.

```{r}
cabinet_turnover %>% 
  count(position)
```

Clearly, there are too many cabinet positions to be legible, so we are picking these few to analyze:  

Secretary of Homeland Security  
EPA Administrator  
Secretary of Health & Human Services  
Secretary of Education  
Secretary of Defense  
Secretary of Labor  
Chief of Staff  

```{r}
specified_cabinet_turnover <- cabinet_turnover %>% 
    filter(position == "Secretary of Homeland Security" | position == "EPA Administrator" | position == "Secretary of Health & Human Services" | position == "Secretary of Education" | position == "Secretary of Defense" | position == "Secretary of Labor" | position == "Chief of Staff")
```

```{r}
ggplot(specified_cabinet_turnover) + geom_boxplot(aes(x=position, y=length))
```


```{r}
cabinet_turnover %>% 
  ggplot() +
  geom_point(aes(x=days, y=length))
```

This doesn't tell us much but it is interesting.  

```{r}
cabinet_turnover %>% 
  ggplot() +
  geom_point(aes(x=days - length, y=length))
```

```{r}
administration_days <- tibble(president = unique(cabinet_turnover$president), admin_total_days = c(1460, 2920, 1460, 2920, 2920, 2920, 730))
```


```{r}
cabinet_turnover %>% 
  mutate(length_proportion = length/(admin_total_days - (days - length)))
```

days-length
*somehow relate to the possible length they could have been there
(proportion of the days of available term that they served) - use this as response?

*look at data within one president?

3) Final models, interpretations, and hypothesis tests  

4) Summary of results  


