---
title: "Analyzing Cabinet Turnover"
author: "Aaron Gould, Lila Craveiro, Danielle Freshwaters"
date: "12/18/2019"
output:
  html_document:
    keep_md: yes
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(faraway) 
library(Sleuth3) 
library(GGally)
library(ggridges)
library(fivethirtyeight)
library(moderndive)
```


## Cabinet Turnover Data

Question: We will be analyzing the data set **cabinet_turnover** from the **fivethirtyeight** package.  This data set includes variables taken from 7 different presidencies, from Jimmy Carter to Donald Trump, summarizing turnover in each of their cabinets.  It was collected from the Federal Government Website News Reports.  Our question is: What factors effect the length of an appointee's cabinet tenure?  We will be evaluating how *position* (the cabinet position), *president* (the sitting president), and a variable of our own creation *days_into_term_start* (number of days into the administration the appointee started) affect *length_proportion* (another variable we created that gives us the proportion of *length* to the total number of days an appointee could have served).  

2) Exploratory work and basic models

*put presidents in choronological order  

```{r}
ggplot(cabinet_turnover) + geom_boxplot(aes(x=president, y= length))
```
We are curious to see how the length each appointee spends in their position depends on the president in office. We will need to take in to account the number of terms each president served and the time that our current president has been in office (this data was taken at Trump's midterm). Without taking that into account we can se that Obama had the highest median for the length an appointee spent in their cabinet position.    


```{r}
ggplot(cabinet_turnover) + geom_boxplot(aes(x=position, y= length)) + coord_flip()
```

*sort by median length  

I wanted to see how many only had one.

```{r}
cabinet_turnover %>% 
  count(position)
```

Clearly, there are too many cabinet positions to be legible, so we are picking these few to analyze:  

Secretary of Homeland Security  
EPA Administrator  
Secretary of Health & Human Services  
Secretary of Education  
Secretary of Defense  
Secretary of Labor  
Chief of Staff  

```{r}
specified_cabinet_turnover <- cabinet_turnover %>% 
    filter(position == "Secretary of Homeland Security" | position == "EPA Administrator" | position == "Secretary of Health & Human Services" | position == "Secretary of Education" | position == "Secretary of Defense" | position == "Secretary of Labor" | position == "Chief of Staff")
```

```{r}
ggplot(specified_cabinet_turnover) + geom_boxplot(aes(x=position, y=length)) + coord_flip()
```

New variable: the number of days into the president's term that the appointee started  

```{r}
new_cabinet_turnover <- cabinet_turnover %>% 
  mutate(days_into_term_start = days - length)
```


```{r}
new_cabinet_turnover %>% 
  ggplot() +
  geom_point(aes(x=days_into_term_start, y=length))
```

This shows that the later into the president's term the appointee started, the shorter the length of their tenure.  The two downward angled lines of points represent those cases that served the maximum length available to them (within the four or eight year term).  

```{r}
administration_days <- tibble(president = unique(new_cabinet_turnover$president), admin_total_days = c(1460, 2920, 1460, 2920, 2920, 2920, 730))

jointdataset <- full_join(new_cabinet_turnover, administration_days, by = "president")
jointdatasetspecified <- full_join(specified_cabinet_turnover, administration_days, by = "president")
```


*length_proportion* is the proportion of *length* to the total number of days an appointee could have served. For example...


```{r}
length_prop_dataset <- jointdataset %>% 
  mutate(length_proportion = length/(admin_total_days - (days_into_term_start)))

length_prop_dataset  %>% 
  select("president", "appointee", "admin_total_days", "length_proportion")
```

```{r}
ggplot(length_prop_dataset) + geom_boxplot(aes(x=president, y= length_proportion))
```

```{r}
length_prop_dataset_specified <- jointdatasetspecified %>% 
  mutate(length_proportion = length/(admin_total_days - (days - length))) %>% 
  select("president", "position", "length_proportion")

length_prop_dataset_specified
```

```{r}
ggplot(length_prop_dataset_specified) + geom_boxplot(aes(x=position, y=length_proportion)) + coord_flip()
```

```{r}
length_prop_dataset %>% 
  ggplot() +
  geom_point(aes(x=days_into_term_start, y=length_proportion))
```


3) Models, interpretations, and hypothesis tests  

```{r}
lm_president <- lm(length_proportion ~ president, data = length_prop_dataset)

get_regression_table(lm_president)
```

Intercept: The average *length_proportion* of an appointee under the Bush41 administration  
presidentBush43 coefficient: The difference in *length_proportion* for an appointee between Bush41 and Bush43 on average  

```{r}
lm_position <- lm(length_proportion ~ position, data = length_prop_dataset_specified)

get_regression_table(lm_position)
```

Intercept: The average *length_proportion* of a Chief of Staff appointee  
positionEPAadministrator: The difference in *length_proportion* between Chief of Staff and EPA Administrator on average  

```{r}
lm_startdate <- lm(length_proportion ~ days_into_term_start, data = length_prop_dataset)

get_regression_table(lm_startdate)
```

The estimate for the *days_into_start* coefficent, and the p-value, is 0.  This reinforces what we could see in the graph.  Basically, there is a strong relationship between *days_into_start* and *length_proportion* of nothing.  In other words, the length of an appointee's tenure does not depend on how far into the president's administration they started.  

```{r}
lm_president_position <- lm(length_proportion ~ president*position, data = length_prop_dataset_specified)

get_regression_table(lm_president_position)
```

Intercept: The average *length_proprtion* for a Chief of Staff appointee under the Bush41 administration  
presidentBush43:positionEPAadministrator: The average change in *length_proportion* between a Chief of Staff appointee and EPA Administrator from Bush41 to Bush43  

$$
H_0: \beta_1 = \beta_2 = \beta_3 = \beta_4 = 0 \\
H_a: \text{at least one of the } \beta_i \ne 0
$$

$H_0$: All coefficients are equal to 0, there is no relationship between *president* and *length_proportion*  

$H_a$: At least one coefficient is not equal to 0, there is a relationship between *president* and *length_proportion*  

```{r}
glance(lm_president) %>% select(r.squared)

r_squared_actual <- glance(lm_president) %>% select(r.squared) %>% pull()
```

```{r}
mod_no_relationship <- lm(length_proportion ~ sample(president), data=length_prop_dataset)
tidy(mod_no_relationship)
glance(mod_no_relationship) %>% select(r.squared)
```

```{r}
set.seed(100)

r_squared <- length_prop_dataset %>% 
  rep_sample_n(size = 312, replace = FALSE, reps = 200) %>% 
  group_by(replicate) %>% 
  do(lm(length_proportion ~ sample(president), data = .) %>% glance()) %>% 
  select(replicate, r.squared)

r_squared
```

```{r}
r_squared %>% 
  ggplot(aes(x=r.squared)) +
  geom_histogram(bins = 20) +
  geom_vline(xintercept = 0.08052376, color="red")
```

This shows that we can reject the null hypothesis.  None of the simulated r.squared values are as extreme as the actual r.squared value.  There is then some relationship between *president* and *length_proportion*.  However, the difference between the most extreme simulated r.squared value and the actual is not significantly large.  

```{r}
lm_lengthprop_null <- lm(length_proportion ~ 1, data = length_prop_dataset)
anova(lm_lengthprop_null, lm_president) %>% tidy()
```

The p-value is about 0.0007, significantly less than 0.05.  This means that there is a strong relationship between *president* and *length_proportion*.  


4) Summary of results  

- we found that *president* has the most significant effect on *length_proportion*, and that *days_into_term_start* has no effect  
- the p-values forthe positions we analyzed were relatively high, indicating little to no relationship between *position* and *length_proportion*, thus we focused on *president*  
- interesting to apply statistics to a subject that is so commonly discussed and analyzed (politics)  
- we had to create multiple new variables and datasets because some of the existing variables were recorded in a way that was unhelpful or irrelevant to our analysis  
- pitfalls included the quantity of positions, and that they weren't all included in every president's administration, some appointees overlapped administrations, there was missing information for some cases (start/end dates)  
- other variables that would have been interesting to analyze had they been included in the data set are party, age, gender, previous political experience  


Next steps: Organize work and make it look nice, add echo=false, look at cases (esp in Trump data) that have n/a, discuss and prepare presentation  




