---
title: "Analyzing Cabinet Turnover"
author: "Aaron Gould, Lila Craveiro, Danielle Freshwaters"
date: "12/18/2019"
output:
  html_document:
    keep_md: yes
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(broom)
library(faraway) 
library(Sleuth3) 
library(GGally)
library(ggridges)
library(fivethirtyeight)
library(moderndive)
```


## Cabinet Turnover Data

**Question:** We will be analyzing the data set **cabinet_turnover** from the **fivethirtyeight** package.  This data set includes variables taken from 7 different presidencies, from Jimmy Carter to Donald Trump, summarizing turnover in each of their cabinets.  It was collected from the Federal Government Website News Reports.  Our question is: **What factors effect the length of an appointee's cabinet tenure?**  We will be evaluating how *position* (the cabinet position), *president* (the sitting president), and a variable of our own creation *days_into_term_start* (number of days into the administration the appointee started) affect *length_proportion* (another variable we created that gives us the proportion of *length* to the total number of days an appointee could have served).  


```{r, echo=FALSE}
ggplot(cabinet_turnover) + geom_boxplot(aes(x= fct_relevel(president, "Carter", "Reagan", "Bush 41", "Clinton", "Bush 43", "Obama", "Trump"), y= length)) + xlab("president")
```


```{r, warning=FALSE, echo=FALSE}
ggplot(cabinet_turnover) + geom_boxplot(aes(x=fct_reorder(position, length, median), y= length)) + coord_flip()
```

Clearly, there are too many cabinet positions to be legible, so we are picking these few to analyze:  

Secretary of Homeland Security  
EPA Administrator  
Secretary of Health & Human Services  
Secretary of Education  
Secretary of Defense  
Secretary of Labor  
Chief of Staff  

```{r, echo=FALSE}
specified_cabinet_turnover <- cabinet_turnover %>% 
    filter(position == "Secretary of Homeland Security" | position == "EPA Administrator" | position == "Secretary of Health & Human Services" | position == "Secretary of Education" | position == "Secretary of Defense" | position == "Secretary of Labor" | position == "Chief of Staff")
```

```{r, warning=FALSE, echo=FALSE}
ggplot(specified_cabinet_turnover) + geom_boxplot(aes(x=position, y=length)) + coord_flip()
```

New variable *days_into_term_start*: the number of days into the president's term that the appointee started  

```{r, echo=FALSE}
new_cabinet_turnover <- cabinet_turnover %>% 
  mutate(days_into_term_start = days - length)
```


```{r, warning=FALSE, echo=FALSE}
new_cabinet_turnover %>% 
  ggplot() +
  geom_point(aes(x=days_into_term_start, y=length))
```

New variable *length_proportion*: the proportion of *length* to the total number of days an appointee could have served. For example...

```{r, echo=FALSE}
administration_days <- tibble(president = unique(new_cabinet_turnover$president), admin_total_days = c(1460, 2920, 1460, 2920, 2920, 2920, 730))

jointdataset <- full_join(new_cabinet_turnover, administration_days, by = "president")
jointdatasetspecified <- full_join(specified_cabinet_turnover, administration_days, by = "president")
```


```{r, echo=FALSE}
length_prop_dataset <- jointdataset %>% 
  mutate(length_proportion = length/(admin_total_days - (days_into_term_start)), 
         chronological_president = fct_relevel(president, "Carter", "Reagan", "Bush 41", "Clinton", "Bush 43", "Obama", "Trump"))

length_prop_dataset  %>% 
  select("president", "appointee", "admin_total_days", "length_proportion")
```

```{r, warning=FALSE, echo=FALSE}
ggplot(length_prop_dataset) + geom_boxplot(aes(x=chronological_president, y= length_proportion)) + xlab("president")
```

```{r, echo=FALSE}
length_prop_dataset_specified <- jointdatasetspecified %>% 
  mutate(length_proportion = length/(admin_total_days - (days - length)),
         chronological_president = fct_relevel(president, "Carter", "Reagan", "Bush 41", "Clinton", "Bush 43", "Obama", "Trump")) %>% 
  select("chronological_president", "position", "length_proportion")
```

```{r, warning=FALSE, echo=FALSE}
ggplot(length_prop_dataset_specified) + geom_boxplot(aes(x=position, y=length_proportion)) + coord_flip()
```

```{r, warning=FALSE, echo=FALSE}
length_prop_dataset %>% 
  ggplot() +
  geom_point(aes(x=days_into_term_start, y=length_proportion))
```


# Models

```{r, echo=FALSE}
lm_president <- lm(length_proportion ~ chronological_president, data = length_prop_dataset)

get_regression_table(lm_president)
```

Intercept: The average *length_proportion* of an appointee under the Carter administration  
chronological_presidentReagan coefficient: The difference in *length_proportion* for an appointee between Reagan and Carter on average  

```{r, echo=FALSE}
lm_position <- lm(length_proportion ~ position, data = length_prop_dataset_specified)

get_regression_table(lm_position)
```

Intercept: The average *length_proportion* of a Chief of Staff appointee  
positionEPAadministrator: The difference in *length_proportion* between Chief of Staff and EPA Administrator on average  

```{r, echo=FALSE}
lm_startdate <- lm(length_proportion*100 ~ days_into_term_start, data = length_prop_dataset)

tidy(lm_startdate)
```

Intercept:  The average *length_proportion* as a percentage for all cabinet positions under all presidents   
The estimate for the *days_into_term_start* coefficient is about 0.015 (as a percent, rather than a decimal).  The p-value is so small, it can be considered 0.  This means that there is a relationship between *days_into_term_start* and *length_proportion* although it is a weak relationship.  

```{r, echo=FALSE}
lm_president_position <- lm(length_proportion ~ chronological_president*position, data = length_prop_dataset_specified)

get_regression_table(lm_president_position)
```

Intercept: The average *length_proprtion* for a Chief of Staff appointee under the Carter administration  
chronological_presidentReagan:positionEPA Administrator: The average change in *length_proportion* between a Chief of Staff appointee and EPA Administrator from Carter to Reagan  

# Hypothesis Tests

*president* vs. *length_proportion*  
$$
H_0: \beta_1 = \beta_2 = \beta_3 = \beta_4 = 0 \\
H_a: \text{at least one of the } \beta_i \ne 0
$$

$H_0$: All coefficients are equal to 0, there is no relationship between *president* and *length_proportion*  

$H_a$: At least one coefficient is not equal to 0, there is a relationship between *president* and *length_proportion*  


```{r, echo=FALSE}
lm_lengthprop_null <- lm(length_proportion ~ 1, data = length_prop_dataset)
anova(lm_lengthprop_null, lm_president) %>% tidy()
```

The p-value is about 0.0007, significantly less than 0.05.  This means that we can reject the null hypothesis and there is a strong relationship between *president* and *length_proportion*.  

Interaction between *president* and *position*  
```{r, echo=FALSE}
lm_presidentposition_null <- lm(length_proportion ~ chronological_president + position, data = length_prop_dataset_specified)

anova(lm_presidentposition_null, lm_president_position) %>% tidy()
```

The p-value here is very high, about 0.98.  This means that we cannot reject the null hypothesis - there could be no interaction between *president* and *position*.  

# Summary of Results  

- we found that *president* has the most significant effect on *length_proportion*, and that *days_into_term_start* has very little effect  

- the p-values for the positions we analyzed were relatively high, indicating little to no relationship between *position* and *length_proportion*, thus we focused on *president*  

- interesting to apply statistics to a subject that is so commonly discussed and analyzed (politics)  

- we had to create multiple new variables and datasets because some of the existing variables were recorded in a way that was unhelpful or irrelevant to our analysis  

- pitfalls included the quantity of positions, and that they weren't all included in every president's administration, some appointees overlapped administrations, there was missing information for some cases (start/end dates)  

- other variables that would have been interesting to analyze had they been included in the data set are party, age, gender, previous political experience  






